Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-10-26 ms/plos_latex.tex
update bib

\bibliography{virulence}
\end{document}

>>>>

\begin{thebibliography}{10}

\bibitem{alizon_virulence_2009}
Alizon S, Hurford A, Mideo N, van Baalen M.
\newblock Virulence evolution and the trade-off hypothesis: history, current
  state of affairs and the future.
\newblock J Evol Biol. 2009;22:245--259.
\newblock doi:{10.1111/j.1420-9101.2008.01658.x}.

\bibitem{EbertBull2003}
Ebert D, Bull JJ.
\newblock Challenging the trade-off model for the evolution of virulence: is
  virulence management feasible?
\newblock Trends Microbiol. 2003;11(1):15--20.

\bibitem{alizon_adaptive_2015}
Alizon S, Michalakis Y.
\newblock Adaptive virulence evolution: the good old fitness-based approach.
\newblock Trends in Ecology \& Evolution. 2015;30(5):248--254.
\newblock doi:{10.1016/j.tree.2015.02.009}.

\bibitem{Dwyer+1990}
Dwyer G, Levin SA, Buttel L.
\newblock A simulation model of the population dynamics and evolution of
  myxomatosis.
\newblock Ecol Monog. 1990;60:423--447.

\bibitem{mackinnon1999genetic}
Mackinnon MJ, Read AF.
\newblock Genetic relationships between parasite virulence and transmission in
  the rodent malaria {{\em Plasmodium chabaudi}}.
\newblock Evolution. 1999; p. 689--703.

\bibitem{jensen2006empirical}
Jensen KH, Little T, Skorping A, Ebert D.
\newblock Empirical support for optimal virulence in a castrating parasite.
\newblock PLoS Biol. 2006;4(7):e197.

\bibitem{deroode2008virulence}
De~Roode JC, Yates AJ, Altizer S.
\newblock Virulence-transmission trade-offs and population divergence in
  virulence in a naturally occurring butterfly parasite.
\newblock Proceedings of the National Academy of Sciences.
  2008;105(21):7489--7494.

\bibitem{Fraser+2007}
Fraser C, Hollingsworth TD, Chapman R, de~Wolf F, Hanage WP.
\newblock Variation in {HIV}-1 set-point viral load: Epidemiological analysis
  and an evolutionary hypothesis.
\newblock PNAS. 2007;104:17441--17446.

\bibitem{fraser_virulence_2014}
Fraser C, Lythgoe K, Leventhal GE, Shirreff G, Hollingsworth TD, Alizon S,
  et~al.
\newblock Virulence and Pathogenesis of {HIV}-1 Infection: An Evolutionary
  Perspective.
\newblock Science. 2014;343(6177):1243727.
\newblock doi:{10.1126/science.1243727}.

\bibitem{shirreff_transmission_2011}
Shirreff G, Pellis L, Laeyendecker O, Fraser C.
\newblock Transmission Selects for {HIV-1} Strains of Intermediate Virulence: A
  Modelling Approach.
\newblock PLoS Computational Biology. 2011;7(10):e1002185.
\newblock doi:{10.1371/journal.pcbi.1002185}.

\bibitem{herbeck_hiv_2014}
Herbeck JT, Mittler JE, Gottlieb GS, Mullins JI.
\newblock An {HIV} Epidemic Model Based on Viral Load Dynamics: Value in
  Assessing Empirical Trends in {HIV} Virulence and Community Viral Load.
\newblock {PLoS} Comput Biol. 2014;10(6):e1003673.

\bibitem{herbeck_evolution_2016}
Herbeck JT, Mittler JE, Gottlieb GS, Goodreau SM, Murphy JT, Cori A, et~al.
\newblock Evolution of {HIV} virulence in response to widespread scale up of
  antiretroviral therapy: a modeling study.
\newblock Virus Evolution. 2016;2(2):vew028.
\newblock doi:{10.1093/ve/vew028}.

\bibitem{day_virulence_2004}
Day T, Proulx SR.
\newblock A General Theory for the Evolutionary Dynamics of Virulence.
\newblock The American Naturalist. 2004;163(4):E40--E63.
\newblock doi:{10.1086/382548}.

\bibitem{alizon_price_2009}
Alizon S.
\newblock The {Price} equation framework to study disease within-host
  evolution.
\newblock Journal of Evolutionary Biology. 2009;22(5):1123--1132.
\newblock doi:{10.1111/j.1420-9101.2009.01726.x}.

\bibitem{champredon_hiv_2013}
Champredon D, Bellan S, Dushoff J.
\newblock {HIV} Sexual Transmission Is Predominantly Driven by Single
  Individuals Rather than Discordant Couples: A Model-Based Approach.
\newblock PLoS ONE. 2013;8(12):e82906.
\newblock doi:{10.1371/journal.pone.0082906}.

\bibitem{dietz_epidemiological_1988}
Dietz K, Hadeler KP.
\newblock Epidemiological models for sexually transmitted diseases.
\newblock Journal of Mathematical Biology. 1988;26(1):1--25.

\bibitem{kretzschmar_effect_1998}
Kretzschmar M, Dietz K.
\newblock The effect of pair formation and variable infectivity on the spread
  of an infection without recovery.
\newblock Mathematical Biosciences. 1998;148(1):83--113.

\bibitem{hollingsworth_hiv1_2008}
Hollingsworth TD, Anderson RM, Fraser C.
\newblock {HIV}-1 Transmission, by Stage of Infection.
\newblock Journal of Infectious Diseases. 2008;198(5):687--693.
\newblock doi:{10.1086/590501}.

\bibitem{omori2015dynamics}
Omori R, Chemaitelly H, Abu-Raddad LJ.
\newblock Dynamics of non-cohabiting sex partnering in sub-{Saharan} {Africa}:
  a modelling study with implications for {HIV} transmission.
\newblock Sexually Transmitted Infections.
  2015;doi:{10.1136/sextrans-2014-051925}.

\bibitem{may_transmission_1988}
May RM, Anderson RM.
\newblock The Transmission Dynamics of Human Immunodeficiency Virus (HIV) [and
  Discussion].
\newblock Philosophical Transactions of the Royal Society of London Series B,
  Biological Sciences. 1988;321(1207):565--607.

\bibitem{delva_connecting_2016}
Delva W, Leventhal GE, Helleringer S.
\newblock Connecting the dots: network data and models in {HIV} epidemiology.
\newblock AIDS. 2016;30(13):2009--2020.
\newblock doi:{10.1097/QAD.0000000000001184}.

\bibitem{blower_drugs_1991}
Blower SM, Hartel D, Dowlatabadi H, Anderson RM, May RM.
\newblock Drugs, Sex and {HIV}: A Mathematical Model for {New York City}.
\newblock Philosophical Transactions of the Royal Society of London B:
  Biological Sciences. 1991;331(1260):171--187.
\newblock doi:{10.1098/rstb.1991.0006}.

\bibitem{ma_estimating_2014}
Ma J, Dushoff J, Bolker BM, Earn DJD.
\newblock Estimating Initial Epidemic Growth Rates.
\newblock Bulletin of Mathematical Biology. 2014;76(1):245--260.
\newblock doi:{10.1007/s11538-013-9918-2}.

\bibitem{wallinga_how_2007}
Wallinga J, Lipsitch M.
\newblock How generation intervals shape the relationship between growth rates
  and reproductive numbers.
\newblock Proceedings of the Royal Society of London B: Biological Sciences.
  2007;274(1609):599--604.
\newblock doi:{10.1098/rspb.2006.3754}.

\bibitem{soetaert_solving_2010}
Soetaert K, Petzoldt T, Setzer RW.
\newblock Solving Differential Equations in {R}: Package {deSolve}.
\newblock Journal of Statistical Software. 2010;33(9):1--25.
\newblock doi:{10.18637/jss.v033.i09}.

\bibitem{wawer2005rates}
Wawer MJ, Gray RH, Sewankambo NK, Serwadda D, Li X, Laeyendecker O, et~al.
\newblock Rates of {HIV}-1 transmission per coital act, by stage of {HIV}-1
  infection, in {Rakai}, {Uganda}.
\newblock Journal of Infectious Diseases. 2005;191(9):1403--1409.

\bibitem{faria_early_2014}
Faria NR, Rambaut A, Suchard MA, Baele G, Bedford T, Ward MJ, et~al.
\newblock The early spread and epidemic ignition of {HIV}-1 in human
  populations.
\newblock Science (New York, NY). 2014;346(6205):56--61.
\newblock doi:{10.1126/science.1256739}.

\bibitem{elderd_uncertainty_2006}
Elderd BD, Dukic VM, Dwyer G.
\newblock Uncertainty in predictions of disease spread and public health
  responses to bioterrorism and emerging diseases.
\newblock Proceedings of the National Academy of Sciences. 2006;103(42):15693
  --15697.
\newblock doi:{10.1073/pnas.0600816103}.

\bibitem{herbeck_is_2012}
Herbeck JT, Müller V, Maust BS, Ledergerber B, Torti C, Di~Giambenedetto S,
  et~al.
\newblock Is the virulence of {HIV} changing? {A} meta-analysis of trends in
  prognostic markers of {HIV} disease progression and transmission.
\newblock AIDS (London, England). 2012;26(2):193--205.
\newblock doi:{10.1097/QAD.0b013e32834db418}.

\bibitem{payne_impact_2014}
Payne R, Muenchhoff M, Mann J, Roberts HE, Matthews P, Adland E, et~al.
\newblock Impact of {HLA}-driven {HIV} adaptation on virulence in populations
  of high {HIV} seroprevalence.
\newblock Proceedings of the National Academy of Sciences.
  2014;111(50):E5393--E5400.
\newblock doi:{10.1073/pnas.1413339111}.

\bibitem{roberts2015impact}
Roberts HE, Goulder PJ, McLean AR.
\newblock The impact of antiretroviral therapy on population-level virulence
  evolution of {HIV}-1.
\newblock Journal of The Royal Society Interface. 2015;12(113):20150888.

\bibitem{herbeck2016evolution}
Herbeck J, Mittler J, Gottlieb G, Goodreau S, Murphy J, Cori A, et~al.
\newblock Evolution of {HIV} virulence in response to widespread scale up of
  antiretroviral therapy: a modeling study.
\newblock bioRxiv. 2016; p. 039560.

\end{thebibliography}
\end{document}
